---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# apportion

<!-- badges: start -->
<!-- badges: end -->

`apportion` provides different apportionment methods for allocating seats across states. These methods are also sometimes used for allocating seats by votes in proportional representation systems.

## Installation

You can install the development version of `apportion` like so:

``` r
remotes::install_github('christopherkenny/apportion')
```

## Example

`apportion` has several apportionment methods, each of which take two required arguments:
- `size`: the number of seats to apportion across units
- `pop`: a vector of population sizes for each unit

```{r example}
library(apportion)
## basic example code
data('state_2020')

app_adams(size = 435, pop = state_2020$pop)
```

Implemented methods include:

- the Adams Method (`app_adams()`)
- the Balinski Young Method (`app_balinski_young()`)
- the Dean Method (`app_dean()`)
- the D'Hondt Method (`app_dhondt()`)
- the Hamilton-Vinton Method (`app_hamilton_vinton()`)
- the Huntington-Hill Method (`app_huntington_hill()`)
- the Jefferson Method (`app_jefferson()`)
- the Webster Method (`app_webster()`)
